%-------------------------
% Resume in Latex
% Author : Mohammad Seraj
% https://github.com/ansariserajmd/mohammadseraj_resume.git

%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{0pt}
\setlength{\columnsep}{1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\usetikzlibrary{svg.path}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \textbf{#1} \hfill \textbf{#2}\par
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------

\begin{center}
    {\Huge \scshape Mohammad Seraj} \\ \vspace{1pt}
    Kapsethi, Varanasi \\ \vspace{1pt}
    \small \href{tel:#}{\raisebox{-0.1\height}{\faPhone}\ \underline{+91-9628104350} ~} \href{mailto:yourname@gmail.com}{\raisebox{-0.2\height}{\faEnvelope}\ \underline{mail.serajansari@gmail.com}} ~ 
\href{https://www.linkedin.com/in/ansariserajmd/}{\raisebox{-0.2\height}{\faLinkedin}\ \underline{LinkedIn}} ~
    \href{https://github.com/mohammadserajansari}{\raisebox{-0.2\height}{\faGithub}\ \underline{Github}} ~

\end{center}
\vspace{0.5mm}

%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart
    \resumeSubheading
    {Indraprastha Institute of Information Technology, Delhi (IIIT D)}{2022 – 2024}
    {M.Tech Computational Biology}{CGPA: 7.96/10}
    \resumeSubheading
    {Hindustan College of Science and Technology Farah, Mathura}{2018 – 2022}
    {B.Tech Biotechnology}{CGPA: 7.8/10}
    \resumeSubheading
    {Dr. AI Memo Sunbeam School, Rohania Varanasi, Uttar Pradesh}{2016 – 2017}
    {12th - CBSE Board}{74\%}
    \resumeSubheading
    {B N S School Kursato, Chaukhandi Varanasi, Uttar Pradesh}{2014 – 2015}
    {High School - CBSE Board}{CGPA: 9.8/10}
\resumeSubHeadingListEnd

% %------RELEVANT COURSEWORK-------
% \section{COURSE WORK}
% \begin{multicols}{4}
%     \begin{itemize}[itemsep=-2pt, parsep=5pt]
%         \item Natural Language Processing (NLP)
%         \item Machine Learning in Biomedical Application
%         \item Big Data Mining in Healthcare
%         \item Biomedical Image Processing
%         \item Object Oriented Programming and Design (Python)
%         \item Research Methods
%         \item Project Management \& Entrepreneurship
%     \end{itemize}
% \end{multicols}
% \vspace*{2.0\multicolsep}


%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\normalsize{Languages:}}{  \normalsize{Python, SQL}} \\
     \textbf{\normalsize{Technologies/Frameworks:}}{  \normalsize{Machine Learning, Deep Learning, Natural Language Processing, Pandas, NumPy, Matplotlib, Seaborn, Scipy, scikit-learn, TensorFlow, PyTorch, Exploratory Data Analysis, Inferential Data Analysis, Tableau, PowerBI, Docker, AWS
}} \\
     \textbf{\normalsize{Developer Tools:}}{  \normalsize{VS Code, PyCharm, Google Colab }} \\
    }}
 \end{itemize}
 \vspace{-15pt}


%-----------PROJECTS-----------
\section{THESIS/PROJECTS}




\resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{\large{\underline{Thesis - Deep learning-based Alzheimer’s disease diagnostics using medical images }}} \large{\textbf{\\ Python, TensorFlow, PyTorch}}\href{https://drive.google.com/file/d/1EKDIsHLkLoA0w_0jGkaA0g-2UfU4z-q5/view}{\raisebox{-0.1\height}{\faExternalLink} $|$ Demo}  $|$} 
    {August 01, 2023 - May 21, 2024}
    \resumeItemListStart
        \resumeItem{\normalsize{Developing specialized deep learning models for medical image analysis, particularly focusing on MRI scans. The goal is to accurately diagnose Alzheimer's disease through multi-class classification and enhance accuracy in identifying different stages of the disease using advanced methodologies.}}

    \resumeItemListEnd



\resumeProjectHeading
{\textbf{\large{\underline{Social Implications of NLP-Driven Healthcare Technologies:}}} \textbf{\large{Empowering Patients through Medicine}} $|$ \large{\textbf{Python, PyTorch}} \href{https://github.com/mohammadserajansari}{\raisebox{-0.1\height}{\faExternalLink}} $|$ \href{https://github.com/mohammadserajansari}{View Code} $|$ }  
{February 2024 -- April 2024}
\resumeItemListStart
    \resumeItem{\normalsize{Leveraged patient feedback and advanced NLP models such as BERT to improve healthcare outcomes and precision by classifying diseases and recommending medications, while also customizing treatments through manual drug annotations.}}
\resumeItemListEnd
\resumeSubHeadingListEnd




\resumeProjectHeading
{\textbf{\large{\underline{Emotionally Augmented Bigram Language Models for Tailored Text Generation}}} \textbf{\large{}} \large{\textbf{\\ $|$ Python, PyTorch}}\href{https://github.com/mohammadserajansari}{\raisebox{-0.1\height}{\faExternalLink} $|$ {View Code}} $|$ }  
{January 29, 2024 -- February 5, 2024}
\resumeItemListStart
    \resumeItem{\normalsize{Developed a predictive language model with bigram analysis and advanced smoothing techniques for accuracy. Incorporated emotion generation to produce text with targeted feelings, enhancing versatility across contexts.}}
\resumeItemListEnd
\resumeSubHeadingListEnd




\resumeProjectHeading
{\textbf{\large{\underline{Developing machine learning and deep learning model for Blood Brain Barrier }}} \textbf{\large{permeability prediction}} {\large{\textbf{$|$ Python, ML, Random Forest, Streamlit}}} \href{https://bbbpredict.streamlit.app/}{\raisebox{-0.1\height} {\faExternalLink} $|$ \textbf{Web App}} $|$  } {June 2023, July 2023}
\resumeItemListStart
    \resumeItem{\normalsize{Developing ML/DL models for BBB permeability with pubchempy, rdkit, and Mordred significantly improves the accuracy of drug brain access. Demonstrating expertise in advancing biomedical and pharmaceutical research through enhanced assessments.}}
\resumeItemListEnd 
\resumeSubHeadingListEnd





\resumeProjectHeading
{\textbf{\large{\underline{Classification of Liver Patients using Machine Learning and Deep Learning }}} \textbf{\large{}} {\large{\textbf{\\ $|$Python, ML, DL}}} \href{https://github.com/mohammadserajansari/-Classification-of-Liver-Patients-using-Machine-Learning-and-Deep-Learning}{\raisebox{-0.1\height} {\faExternalLink} $|$ \textbf{View Code}} $|$  } {June 2023, July 2023}
\resumeItemListStart
    \resumeItem{\normalsize{Leveraged genomics data analysis with machine and deep learning for precise liver cancer detection, advancing diagnostic accuracy and disease identification strategies.}}
\resumeItemListEnd 
\resumeSubHeadingListEnd


\newpage

\resumeProjectHeading
{\textbf{\large{\underline{Classification of Proteins using pfeature and Model Prediction}}} \textbf{\large{with Machine Learning/Deep Learning}} {\large{\textbf{$|$ Python, ML, DL}}} \href{https://github.com/mohammadserajansari/Classification-of-Proteins-using-pfeature-and-Model-Prediction-with-Machine-Learning-Deep-Learning}{\raisebox{-0.1\height} {\faExternalLink} $|$ \textbf{View Code}} $|$  } {June 2023, July 2023}
\resumeItemListStart
    \resumeItem{\normalsize{Utilized pfeature for protein feature extraction, applied machine learning/deep learning models to classify proteins, achieving accurate predictions.}}
\resumeItemListEnd 
\resumeSubHeadingListEnd



%-----------EXPERIENCE-----------
\section{INTERNSHIP}
  \resumeSubHeadingListStart

    \resumeSubheading
      {MRD Life Science Pvt. Ltd. \href{certificate Link}{\raisebox{-0.1\height}\faExternalLink }}{June 2021 -- July 2021} 
      {\underline{Intern}}{Gomti nagar, Lucknow 226010}
      \resumeItemListStart
        \resumeItem{\normalsize{Hands – on industrial training with state of art lectures on Real Time PCR (RT PCR), High Performance Liquid Chromatography (HPLC), PCR, Gel Doc System and Bioreactor.}}
  
      \resumeItemListEnd  
      
  \resumeSubHeadingListEnd
\vspace{-12pt}


% -----------EXPERIENCE-----------
\section{WORK EXPERIENCE }
  \resumeSubHeadingListStart

    \resumeSubheading
      {Indraprastha Institute of Information Technology, Delhi (IIIT D)  \href{certificate Link}{\raisebox{-0.1\height}\faExternalLink }}{August 2022 -- May 2024} 
      {\underline{Teaching Assistant}}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{\normalsize{Communication Skills: Assisted in facilitating interactive sessions to enhance students' verbal and written communication abilities.}}
        \resumeItem{\normalsize{Basic Electronics: Provided guidance and support to students in understanding fundamental concepts and practical applications in basic electronics coursework.}}
        \resumeItem{\normalsize{Academic Work: Volunteered for the organization and administration of the PGCAT exam organized by IIIT D, ensuring a smooth testing experience for candidates.}}
        \resumeItem{\normalsize{Nation and Her Narratives: Engaged students in discussions and activities centered around understanding historical and cultural narratives, fostering critical thinking and analytical skills.}}
  
      \resumeItemListEnd  
  \resumeSubHeadingListEnd
\vspace{-12pt}



\section{ACHIEVEMENTS }
      \resumeItemListStart
        \resumeItem{\normalsize{DBT GAT-B (2022) Exam: Achieved All India Rank 133.}}
      \resumeItemListEnd  
  \resumeSubHeadingListEnd
\vspace{-12pt}



\vspace{30\medskipamount}

Declaration: The above information is correct to the best of my knowledge.

\medskip

\noindent Mohammad Seraj \\
Date: \today







\end{document}

